### 2020-12-15 README.Rmd
add

- `add_capital_distance()`: adds capital-to-capital distance (in kilometers, "as the crow flies") to dyad-year or state-year data.
- `add_contiguity()`: adds Correlates of War direct contiguity data to dyad-year or state-year data.
- `add_cow_majors()`: adds Correlates of War major power information to dyad-year or state-year data.
- `add_democracy()`: adds estimates of democracy/levels of democracy to dyad-year or state-year data.
- `create_stateyears()`: converts Correlates of War or Gleditsch-Ward state membership data into state-year format.
- `create_dyadyears()`: converts Correlates of War or Gleditsch-Ward state system membership data into dyad-year format.
- `filter_prd()`: filters dyad-year data frame to just "politically relevant" dyads.

@@

- `capitals`: a list of capitals and capital transitions for Correlates of War state system members
- `ccode_democracy`: Correlates of War state-year data with three different estimates of democracy (Varieties of Democracy, Polity, Xavier Marquez/Pemstein et al.'s "(Quick) Unified Democracy Scores").
- `cow_contdir`: Correlates of War Direct Contiguity Data (v. 3.2)
- `cow_ddy`: a full directed dyad-year data frame of Correlates of War state system members
- `cow_gw_years`: a yearly data frame including information about Correlates of War and Gleditsch-Ward states.
- `cow_majors`: Correlates of War major powers data (version: 2016)
- `cow_states`: Correlates of War state system membership data (version: 2016)
- `gw_ddy`: a full directed dyad-year data frame of Gleditsch-Ward state system members
- `gw_states`: Gleditsch-Ward independent state system data (version: 2017)
- `maoz_powers`: Zeev Maoz' global/regional power data.

>>>>

- `add_capital_distance()`: adds capital-to-capital distance (in kilometers, "as the crow flies") to dyad-year or state-year data.
- `add_contiguity()`: adds Correlates of War direct contiguity data to dyad-year or state-year data.
- `add_cow_majors()`: adds Correlates of War major power information to dyad-year or state-year data.
- `add_democracy()`: adds estimates of democracy/levels of democracy to dyad-year or state-year data.
- `add_gwcode_to_cow():` adds Gleditsch-Ward state codes to dyad-year or state-year data with Correlates of War state codes.
- `create_stateyears()`: converts Correlates of War or Gleditsch-Ward state membership data into state-year format.
- `create_dyadyears()`: converts Correlates of War or Gleditsch-Ward state system membership data into dyad-year format.
- `filter_prd()`: filters dyad-year data frame to just "politically relevant" dyads.

@@

- `capitals`: a list of capitals and capital transitions for Correlates of War state system members
- `ccode_democracy`: Correlates of War state-year data with three different estimates of democracy (Varieties of Democracy, Polity, Xavier Marquez/Pemstein et al.'s "(Quick) Unified Democracy Scores").
- `cow_alliance`: directed dyad-year alliance formation data from the Correlates of War
- `cow_contdir`: Correlates of War Direct Contiguity Data (v. 3.2)
- `cow_ddy`: a full directed dyad-year data frame of Correlates of War state system members
- `cow_gw_years`: a yearly data frame including information about Correlates of War and Gleditsch-Ward states.
- `cow_majors`: Correlates of War major powers data (version: 2016)
- `cow_states`: Correlates of War state system membership data (version: 2016)
- `gw_ddy`: a full directed dyad-year data frame of Gleditsch-Ward state system members
- `gw_states`: Gleditsch-Ward independent state system data (version: 2017)
- `maoz_powers`: Zeev Maoz' global/regional power data.
